---
title: "Sample analysis code"
output: html_document
date: "2023-09-19"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("here")
library("tidyverse")
library("afex")
library("ggplot2")
library("car")
```

## Overview of the dataset

This sample dataset is based on the following experimental design:
There are two within-subject factors: 
factor 1 stimuli type: picture condition vs. text condition
factor 2 test phase: testing 1 vs. testing 2
There are also two DVs: edit distance score and accuracy score

## Load data
```{r}
data_accuracy = read.csv("data_accuracy.csv")

# data transformation: creating new derieved variables
data_accuracy = data_accuracy %>%
  mutate(accuracy_pass_threshold = ifelse(accuracy_score > 0.5, 1, 0))
```

## Aggregate data
```{r}

# subject-level data
data_subj = data_accuracy %>%
  group_by(id, phase, condition) %>%
  summarise(mean_subj = mean(accuracy_score))

# condition-level data 
data_condition = data_subj %>%
  group_by(condition, phase) %>%
  summarise(mean_condition = mean(mean_subj),
            se = sd(mean_subj)/sqrt(n()))
```

## Plotting (conditional-level)
```{r}
ggplot(data_condition, aes(x = condition, y = mean_condition, fill = phase, group = phase)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_errorbar(aes(ymin = mean_condition - se, ymax = mean_condition + se),
                width = 0.25, 
                position = position_dodge(width = 0.8)) +
  labs(title = "Clustered Bar Graph with Error Bars", y = "Mean Value") +
  theme_minimal()
```
## Plotting (trial and subject level)
```{r}
ggplot(data_accuracy, aes(x = trial_id, y = accuracy_score)) +
  geom_line(color = "red") + 
  labs(title = "Accuracy by Trial Number", x = "Trial Number", y = "Accuracy") +
  theme_minimal() +
  theme(legend.position = "none") + 
  facet_wrap(~id)
```
## Stats: LMM
```{r}
# set contrast
set_sum_contrasts()

###### DV: continuous ##########
# random intercept only model
mixed(accuracy_score ~ condition * phase + (1|id) + (1|trial_id), data = data_accuracy)

######## DV: binary variable ####### 
# random intercept model
mixed(accuracy_pass_threshold ~ condition * phase + (1|id) + (1|trial_id), 
      family = binomial(link = "logit"), method = "LRT",data = data_accuracy)
```